Constructing the transition graphs of interacting hysterons

### 2022-06-13 Paper_draft.tex
Added bibliography file and 4 citations

Frustrated media can have rugged energy landscapes, with many metastable states. Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving. For a variety of systems, including sheared amorphous solids (Nagel, 2021; Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets (Bense, 2021) and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\ 
It turns out that the response of many frustrated systems can be captured by an interacting collection of hysteretic two-state elements, called hysterons. The hysteron model, first suggested by Ferenc Preisach (Preisach, 1935), has long been used to model hysteretic systems as a collection of small hysteretic two-state elements. However, the Preisach model considers hysterons to be independent, while the interacting hysteron model has remained largely unexplored. The recent experimental findings show that the interacting hysteron model is relevant for many physical systems, and thus worth examining in more detail.\\
The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving (Regev, 2019). Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons. For as few as three interacting hysterons, over 15,000 distinct graphs are found (Van Hecke, 2021). Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\

@@

\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
\begin{equation}
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
\end{equation}
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
%\bibliography{apssamp}% Produces the bibliography via BibTeX.

>>>>

Frustrated media can have rugged energy landscapes, with many metastable states. Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving. For a variety of systems, including sheared amorphous solids\cite{lindeman2021}( Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets\cite{bense2021} and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\ 
It turns out that the response of many frustrated systems can be captured by an interacting collection of hysteretic two-state elements, called hysterons. The hysteron model, first suggested by Ferenc Preisach\cite{preisach1935}, has long been used to model hysteretic systems as a collection of small hysteretic two-state elements. However, the Preisach model considers hysterons to be independent, while the interacting hysteron model has remained largely unexplored. The recent experimental findings show that the interacting hysteron model is relevant for many physical systems, and thus worth examining in more detail.\\
The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving (Regev, 2019). Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons. For as few as three interacting hysterons, over 15,000 distinct graphs are found\cite{vhecke2021}. Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\

@@

\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
\begin{equation}
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
\end{equation}
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}

\bibliography{test}% Produces the bibliography via BibTeX.
